---
title: "Project"
author: "Rachel Rhodes"
date: "`r Sys.Date()`"
output:
  html_document: 
    theme: spacelab
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Section 1:
This section illustrates how we loaded the data, assessed the data structure, and cleaned the data. 
_Load Library_
```{r}
library(tidyverse)
library(RColorBrewer)
library(paletteer)
library(janitor)
library(here)
library(naniar)
```

```{r}
getwd()
```

1. Load the data. 
```{r}
indian_food <- read_csv(here("Project", "Data", "indian_food.csv")) %>% janitor::clean_names()
```

```{r}
indian_food
```

2. Structure of the data. 
```{r}
glimpse(indian_food)
```

```{r}
summary(indian_food)
```

What are the variables? 
```{r}
names(indian_food)
```

Dealing with NA's
_NA's in data is symbolized by a "-1"_
```{r}
indian_food<-indian_food%>%
  na_if("-1")
```

Counting Number of NA's
```{r}
naniar::miss_var_summary(indian_food)
```

_Split Ingredients Into Their Own Row_
We noticed that the ingredients were listed in one row, so we separated them into their own rows. 
```{r}
indian_food<-indian_food%>%
  mutate_all(tolower)%>%
  transform(ingredients=str_split(ingredients,","))%>%
  unnest(ingredients)
indian_food
```
Adding Total Cook Time column which combines cook time and prep time. 
```{r}
indian_food<-indian_food%>%
  mutate(total_cook_time=as.numeric(cook_time)+as.numeric(prep_time))
indian_food
```

##Section Two: Questions about the data.
Questions for plots:
3. flavor in relationship to diet
7. state/region --> flavor profile

3. What is the relationship between flavor and diet (i.e. is there more spicy dishes in non-vegetarian compared to vegetarian?)

```{r}
flavor_diet <- indian_food %>% 
  filter(!is.na(flavor_profile)) %>%
  ggplot(aes(x=flavor_profile, fill=diet))+
  geom_bar(na.rm=T, position="dodge",alpha=0.75, color="black") + 
  labs(title = "Flavor in Relationship to Diet",
       x = "Flavor Profile",
       y = "Count") +
  theme(plot.title = element_text(size = rel(1.5), hjust = 0.5))
flavor_diet
```

Yes
```{r}
flavor_diet2 <- indian_food %>% 
  filter(!is.na(flavor_profile)) %>%
  ggplot(aes(x=diet, fill=flavor_profile))+
  geom_bar(na.rm=T, position="dodge",alpha=0.75, color="black") +
  labs(title = "Flavor in Relationship to Diet",
       x = "Diet",
       y = "Count") +
  theme(plot.title = element_text(size = rel(1.5), hjust = 0.5))
flavor_diet2
```

7. What flavor profile is more associated with which region/state?

```{r}
flavor_state <- indian_food %>% 
  filter(!is.na(flavor_profile)) %>%
  filter(!is.na(state)) %>%
  ggplot(aes(x=flavor_profile, fill=state))+
  geom_bar(na.rm=T, position="dodge",alpha=0.75, color="black") +
  labs(title = "Flavor in Relationship to State",
       x = "Flavor Profile",
       y = "Count") +
  theme(plot.title = element_text(size = rel(1.0), hjust = 0.5))
flavor_state
```

Yes
```{r}
flavor_state2 <- indian_food %>% 
  filter(!is.na(flavor_profile)) %>%
  filter(!is.na(state)) %>%
  ggplot(aes(x=state, fill=flavor_profile))+
  geom_bar(na.rm=T, position="dodge",alpha=0.75, color="black") +
  labs(title = "Flavor in Relationship to State",
       x = "State",
       y = "Count") +
  theme(plot.title = element_text(size = rel(1.0), hjust = 0.5))+
   theme(axis.text.x = element_text(angle = 60, hjust = 1)) 
flavor_state2
```

```{r}
flavor_region <- indian_food %>% 
  filter(!is.na(flavor_profile)) %>%
  filter(!is.na(region)) %>%
  ggplot(aes(x=flavor_profile, fill=region))+
  geom_bar(na.rm=T, position="dodge",alpha=0.75, color="black") +
  labs(title = "Flavor in Relationship to Region",
       x = "Flavor Profile",
       y = "Count") +
  theme(plot.title = element_text(size = rel(1.0), hjust = 0.5))
flavor_region
```

Yes
```{r}
flavor_region2 <- indian_food %>% 
  filter(!is.na(flavor_profile)) %>%
  filter(!is.na(region)) %>%
  ggplot(aes(x=region, fill=flavor_profile))+
  geom_bar(na.rm=T, position="dodge",alpha=0.75, color="black") +
  labs(title = "Flavor in Relationship to Region",
       x = "Region",
       y = "Count") +
  theme(plot.title = element_text(size = rel(1.0), hjust = 0.5))
flavor_region2
```
